### 2013-09-15 fig_mr_arfi_volumes.tex
updated figures for CORRECT weights and just using EPS with epstopdf LaTeX package

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes.pdf} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volume_diff.pdf} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_total_diff.pdf} \\
(a) Central:Peripheral Volume & (b) Total Volume Difference & (c) Central:Total Volume Difference\\
\end{tabular}
\caption{Comparison of MR and ARFI zonal anatomy volume estimates from manually-segmented images.  Total prostate volumes ranged from 19.6--71.0 cm$^3$ based on MR image models (a), with ARFI image models overestimating total prostate volume by 36.7 $\pm$ 27.9\% (b).  ARFI image delineation of the central zone volume relative to total prostate volume showed a mean underestimation of -15.3 $\pm$ 13.0\% (c, green) relative to the MR central gland : total volume ratios (c, blue).}
\label{fig:mr_arfi_volumes} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volume_diff} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_total_diff} \\
(a) Central:Peripheral Volume & (b) Total Volume Difference & (c) Central:Total Volume Difference\\
\end{tabular}
\caption{Comparison of MR and ARFI zonal anatomy volume estimates from manually-segmented images.  Total prostate volumes ranged from 19.6--71.0 cm$^3$ based on MR image models (a), with ARFI image models overestimating total prostate volume by 36.7 $\pm$ 27.9\% (b).  ARFI image delineation of the central zone volume relative to total prostate volume showed a mean underestimation of -15.3 $\pm$ 13.0\% (c, green) relative to the MR central gland : total volume ratios (c, blue).}
\label{fig:mr_arfi_volumes} 
\end{figure}

### 2013-09-15 fig_mr_arfi_weight.tex
updated figures for CORRECT weights and just using EPS with epstopdf LaTeX package

\begin{figure}[htb!]
\centering
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol.pdf} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol.pdf} &
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol.pdf} \\
(a) Image Volume : Prostate Weight & (b) Image Volume : Path Volume & (c) Path Weight : Path Volume \\
\end{tabular}
\caption{The prostates analyzed in this study showed no significant correlation
    between their measured excised pathology weight (a) and the reconstructed
    volumes in T2WI MR (blue) and ARFI imaging (green).  The coefficients of
    determination (R$^2$) for the linear regressions for each imaging modality
    were 0.05 and 0.13, respectively, indicating no significant correlation.
    Tri-axial pathology measurements were used to make an ellipsoidal prostate
    volume approximation (b), which showed mild correlation with T2WI MR (R$^2$
    = 0.32) and moderate correlation with ARFI imaging (R$^2$ = 0.71).  The
    lack of correlationed between imaging volumes and prostate weight is not
    surprising since the weights were also not correlated with the estimated
    ellipsoidal prostate volumes (c, R$^2$ = 0.04).} 
\label{fig:mr_arfi_weight}
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} \\
(a) Image Volume : Prostate Weight & (b) Image Volume : Path Volume & (c) Path Weight : Path Volume \\
\end{tabular}
\caption{The prostates analyzed in this study showed no significant correlation
    between their measured excised pathology weight (a) and the reconstructed
    volumes in T2WI MR (blue) and ARFI imaging (green).  The coefficients of
    determination (R$^2$) for the linear regressions for each imaging modality
    were 0.05 and 0.13, respectively, indicating no significant correlation.
    Tri-axial pathology measurements were used to make an ellipsoidal prostate
    volume approximation (b), which showed mild correlation with T2WI MR (R$^2$
    = 0.32) and moderate correlation with ARFI imaging (R$^2$ = 0.71).  The
    lack of correlationed between imaging volumes and prostate weight is not
    surprising since the weights were also not correlated with the estimated
    ellipsoidal prostate volumes (c, R$^2$ = 0.04).} 
\label{fig:mr_arfi_weight}
\end{figure}
